Efficient Handling of String-Number Conversion

### 2020-04-05 final-version/main.tex
add two references
more acks

It is not difficult to see from the examples above that, if $\dr(x)$ is an arbitrary PFA with $m$ loops, the formula that defines the number $n$ contains at least $m$ exponential components, one for each loop.
To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open. The problem is difficult even for the case that variables are real numbers. For example, the algorithm in~\cite{kincaid2019closed} involves a quantifier elimination procedure which is double-exponential to the length of the input formula and hence cannot handle large instances. We therefore do not expect that such constraint can be solved efficiently. Instead, we will define a special form of the flat restriction $\dr(x)$ of $x$ that leads to an easier linear formula.

@@

\begin{acks}
This research was  partially supported by the  Swedish Foundation for Strategic Research, Ministry of Science and Technology Project, Taiwan (no. 106-2221-E-001 -009 -MY3), and Ministry of Education, Youth and Sports of Czech Republic (no. LL1908).
\end{acks}

>>>>

It is not difficult to see from the examples above that, if $\dr(x)$ is an arbitrary PFA with $m$ loops, the formula that defines the number $n$ contains at least $m$ exponential components, one for each loop.
To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open. The problem is difficult even for the case that variables are real numbers~\cite{GanCDXZ15,GanCLXZ18}. For example, the algorithm in~\cite{kincaid2019closed} involves a quantifier elimination procedure which is double-exponential to the length of the input formula and hence cannot handle large instances. We therefore do not expect that such constraint can be solved efficiently. Instead, we will define a special form of the flat restriction $\dr(x)$ of $x$ that leads to an easier linear formula.

@@

\begin{acks}
This research was  partially supported by the  Swedish Foundation for Strategic Research, Ministry of Science and Technology Project, Taiwan (no. 106-2221-E-001 -009 -MY3), Ministry of Education, Youth and Sports of Czech Republic (project IT4Innovations excellence in science--LQ1602 and project LL1908), and FIT BUT internal grant FIT-S-20-6427.

\end{acks}
